Model of lens candidates from Space Warps CFHTLS

### 2016-07-11 paper2.tex
more text

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

@@

\newcommand{\figref}[1]{Figure \ref{fig:#1}}

@@

In this section, we discuss ten systems.

\begin{figure}
  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \caption{SW05.  See text in Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}

\begin{figure}
  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
  \caption{SW28}
  \label{fig:SW28}
\end{figure}

\begin{figure}
  \inclfign{SW02}{ASW000619d_011489}
  \caption{SW02}
  \label{fig:SW02}
\end{figure}

\begin{figure}
  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
  \caption{SW09}
  \label{fig:SW09}
\end{figure}

\begin{figure}
  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
  \caption{SW29}
  \label{fig:SW29}
\end{figure}

\begin{figure}
  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
  \caption{Models of SW42, a doubtful candidate because of an
    implausible mass ratio. (See text for details.)}
  \label{fig:SW42}
\end{figure}

\begin{figure}
  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
  \caption{SW58}
  \label{fig:SW58}
\end{figure}

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
  \caption{SW19}
  \label{fig:SW19}
\end{figure}

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
  \caption{SW36}
  \label{fig:SW36}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
  \caption{SW57}
  \label{fig:SW57}
\end{figure}

Each of Figures~\figref{SW05}--\figref{SW57} show six panels, as
follows.

\begin{itemize}

\item The upper left panel show a cutout of the Space~Warps image,
  marked up with a spaghetti diagram.

\item Middle left is a contour map of the arrival-time surface after
  modelling.

\item Lower left is synthetic image.
  Figures~\figref{SW05}--\figref{SW29} include source fitting.
  Figures~\figref{SW42}--\figref{SW57} uses a simple conical
  profile.

\item Upper right is a mass map.

\item Middle right shows a circularly averaged profile of
  $\kappa$.\todo{Fix distance factor in $\kappa$.}

\item Lower right shows stellar vs stellar mass.\todo{which population
  model?}  Abundance matching \citep{2010ApJ...710..903M}.

\end{itemize}

\begin{itemize}

\item Figures~\figref{SW28}--\figref{SW29} show the five most
  convincing lens candidates. SW28 shown in Figure~\figref{SW28} is
  modelled as an arc with three blended images plus a saddle-point
  closer to the galaxy.  SW05 shown in Figure~\figref{SW05} has four
  distinct images (two close to blending).  SW02, SW09 and SW29
  (Figures~\figref{SW02}--\figref{SW29}) have similar
  configurations, with a minimum furthest from the galaxy and three
  images blended into an arc.  All five would be massive ellipticals;
  SW05 is the most massive of all the candidates, with a galaxy-group
  scale mass.

\item Figure~\figref{SW42} shows a candidate that modelling indicates
  is doubtful.  The images appears to have a similar morphology to the
  last three mentioned.  The implied mass, however, is implausibly
  high.\todo{Check photometry of this candidate.}

\item Figures~\figref{SW58} and \figref{SW19} appear plausible lens
  candidates.  Their morphology is similar to SW28, but the
  saddle-point counterimage is not visible.  We consider these lenses
  plausible but less convincing.

\item Figures~\figref{SW36} and \figref{SW57} shows {\em unclear\/}
  cases where modelling failed.

\end{itemize}

@@

\begin{enumerate}
\item Image morphology.
\item Whether images unblended.
\end{enumerate}

Throu visual inspection of the most popular models generated for each candidate and data generated by those models we classified the candidates in four categories.
The data available is shown in \figref{SW58}.
\todo{better explain criterias?}
The following sections list all the models for all the categories, each with a short explanation of the reasons.
Additionally, selected models are presented in figures for demonstration.

\subsection{plausible}

The plausible candidates fail in one category, but are quite convincing in all the others.
One particular reason for a candidate to end up in this category is that is has extended arcs, what is hard to modell with the current version of the program.
Thats why we recomend them for a following up study, for example for taking spectras or other follow up obersatories and for other modelling programs for a try.

\subsection{unclear}

This categy contains the ones that are hard to say.
They might look like lenses visually, but the modelling failed or prediced additional images.

\subsection{convincing}

The candidates that looked the most promising and left little doubt about being lenses were grouped into the category ``convincing''.
In Figures \figref{SW02} to \figref{SW29} we show all the convincing candidates.
Following we list the parameters, obtained applying the technique described in section~\ref{sec:parameter}

\lenstitle{SW02 (ASW000619d)}
Nice arc with counter image;
additional mass at 12 o'clock doesn't seem to influence the image.
\params{1.04}{0.32}{-5.18}

\lenstitle{SW05 (ASW0007k4r)}
The model predicts very steep central mass profile, and thus a very high lensing mass;
looks otherwise very convincing.
\params{3.80}{0.15}{52.50}

\lenstitle{SW09 (ASW0002asp)}
\params{1.12}{0.00}{88.39}

\lenstitle{SW28 (ASW0007xrs)}
Faint, but clearly visible arc and counter image;
but model sfits nicely
\params{1.04}{0.33}{66.63}

\lenstitle{SW29 (ASW0008qsm)}
Faint close arc, but reconstruion works very well;
parameterisation of ellypticity fails.
\params{0.73}{0.00}{249.80}

\subsection{doubtful}

SW42

\subsection{missing}

Finally this category lists all the candidates, that miss redshift measurements of the lens and thus further analysis is difficult.

\lenstitle{SW03 (ASW0006mea)}
\lenstitle{SW14 (ASW0004xjk)}
\lenstitle{SW25 (ASW00007mq)}
\lenstitle{SW30 (ASW0002p8y)}
\lenstitle{SW37 (ASW00086xq)}
\lenstitle{SW39 (ASW0005qiz)}
\lenstitle{SW40 (ASW0008wmr)}
\lenstitle{SW48 (ASW0000g95)}
\lenstitle{SW49 (ASW00007ls)}
\lenstitle{SW50 (ASW00008a0)}
\lenstitle{SW55 (ASW0007t5y)}
\lenstitle{SW59 (ASW00085cp)}

@@

\section{Discussion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand{\inclfig}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img3_ipol}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\inclfign}[2]{
  \centering
	\includegraphics[width=\smallwidth]{spaghetti/#2_input}%
	\includegraphics[width=\smallwidth]{img/nsynth/#2_nsynth}
	\includegraphics[width=\smallwidth]{spaghetti/#2_img1}%
	\includegraphics[width=\smallwidth]{spaghetti/#2_img2}
	\includegraphics[width=\smallwidth]{img/M_encl/#2_M_encl}%
	\includegraphics[width=\smallwidth]{masses/#1_#2_mstel_vs_mtot}
}

@@

\newcommand{\figref}[1]{\ref{fig:#1}}

@@

In this section we show modelling results for ten of the lens
candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
are the most convincingly modelled systems.  The next three cases
(Figures~\figref{SW42},\figref{SW58}) are less good but still very
plausible models, and are representative of the majority of the
sample.  The last two are examples where the models were unconvincing
(Figures~\figref{SW36}) or completely failed (\figref{SW57}).

\begin{figure}
  \inclfign{SW05}{ASW0007k4r_AJIBCHQ6EM}
  \caption{Model results for SW05 (J143454.4+522850).  See text in
    Section~\ref{sec:examples} for details.}
  \label{fig:SW05}
\end{figure}

\begin{figure}
  \inclfign{SW28}{ASW0007xrs_JHC3J2HYV7}
  \caption{Model results for SW28 (J143055.9+572431).}
  \label{fig:SW28}
\end{figure}

\begin{figure}
  \inclfign{SW02}{ASW000619d_011489}
  \caption{Model results for SW02 (J140522.2+574333).}
  \label{fig:SW02}
\end{figure}

\begin{figure}
  \inclfign{SW09}{ASW0002asp_5EKMWWVJHL}
  \caption{Model results for SW09 (J020832.1-043315).}
  \label{fig:SW09}
\end{figure}

\begin{figure}
  \inclfign{SW29}{ASW0008qsm_TOFS7JNGEK}
  \caption{Model results for SW29 (J143838.1+572647).}
  \label{fig:SW29}
\end{figure}

\begin{figure}
  \inclfig{SW42}{ASW00096rm_4Q3YCEWGLN}
  \caption{Modelling results for SW42 (J221716.5+015826).}
  \label{fig:SW42}
\end{figure}

\begin{figure}
  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
  \caption{Model results for SW58 (J143651.6+530705).}
  \label{fig:SW58}
\end{figure}

\begin{figure}
  \inclfig{SW19}{ASW0001ld7_OS3CYAKLRT}
  \caption{Model results for SW19 (J020642.0-095157).}
  \label{fig:SW19}
\end{figure}

\begin{figure}
  \inclfig{SW36}{ASW000096t_7IPP7LWVOF}
  \caption{Model results for SW36 (J090248.4-010232).}
  \label{fig:SW36}
\end{figure}

\begin{figure}
  \inclfig{SW57}{ASW0008pag_5SXGXQYY6V}
  \caption{Model results for SW57 (J143631.5+571131).}
  \label{fig:SW57}
\end{figure}

Let us first consider Figure~\figref{SW05}, which shows model results
from SW05 (J143454.4+522850).

\begin{enumerate}
\item In the upper row we have first a cutout of the Space~Warps
  image, marked up with a spaghetti diagram.  There are four distinct
  lensed images, and the spaghetti diagram proposes that they are a
  minimum nearest to the lensing galaxy, a close minimum-saddle pair,
  and a minimum further away. In Table~\ref{tab:models} we refer to
  such configurations as `$1+2+1$'.
\item Alongside is a synthetic image produced by modelling.  In it,
  the fitted lensed images are shown in colour, while the lensing
  galaxy and extraneous objects have been reduced to grayscale.  These
  two panels are qualitative and display no units, and moreover, the
  mutual alignment of the two panels is only approximate.
\item The middle row shows contour maps from the model.  At middle
  left, we have the arrival-time surface.
\item At middle right we have the mass distribution in the usual
  dimensionless form $\kappa$.  Again, these two panels are mainly
  qualitative: both panels are spatially registered and centred on the
  density-peak of the lens, but no scales have been included.
\item The base row supplies spatial and mass scales.  The left panel
  shows the circularly-averaged $\kappa$ of the model ensemble, with
  increasing radius (in arcsec).  The four short vertical lines
  correspond to the minima and saddle points marked in the upper-left
  panel.  The effective Einstein radius is also shown.  As the radius
  scale indicates SW05 is comparatively large lens on the
  sky.\todo{Fix distance factor in $\kappa$.}
\item Lower right shows the total mass in the model against the
  estimated stellar mass, alongside the values for the whole sample.
  The lower-right shaded region is unphysical according to the
  stellar-population models, because it gives $M<\Mstel$. The
  upper-left shaded region is unphysical according to abundance
  matching, because it gives $M>\Mhalo$.  That is to say, the unshaded
  region is $0<\haloindex<1$.
\end{enumerate}

Proceeding to Figure~\figref{SW28}, we have one image close to the
galaxy and an arc further away, which is interpreted as a blend of
three images (a saddle point with two minima on either side).  We call
this a '1+3' configuration.  It is an indication of a mass
distribution elongated along the arc-counterimage direction (along EW
in this case).

In Figures~\figref{SW02}--\figref{SW29} we see three candidates with
an arc close the lensing galaxy and one image further away.  The arc
is interpreted three images (a minimum with two saddle points on
either side).  We call this a '3+1' configuration.  It is an
indication of a mass distribution elongated perpendicular to the
arc-counterimage direction.

Figures~\figref{SW02}--\figref{SW29} (SW05, SW28, SW02, SW09 and SW29)
all correspond to the mass range of massive ellipticals.  SW05 is the
most massive of all the candidates, with a galaxy-group scale mass.

Figure~\figref{SW42} shows SW42.  The image morphology is similar to
SW05 in Figure~\figref{SW05}, but the lens is much smaller on the sky,
and the inferred mass is at the low end of the sample.  (The synthetic
image shown is cruder than for the five previous figures, but that
does not influence the mass models.)  If these preliminary findings
are confirmed by follow-up observations, this could be the most
dark-matter dominated lens known.\todo{Check photometry of this
  candidate.}

Figures~\figref{SW58} and \figref{SW19} appear plausible lens
candidates.  Their morphology is similar to SW28, but the saddle-point
counterimage is not visible.  We consider these lenses plausible but
less convincing.

Figures~\figref{SW36} and \figref{SW57} are cases where modelling
failed.

@@

\begin{enumerate}
\item The image morphology concisely described: D for double, and
  quads in sub-categorised in four ways
  \citep[cf.][]{2003AJ....125.2769S} as LQ for long-axis quads (as in
  Figure~\figref{SW28}), SQ for short-axis quads (as in
  Figure~\figref{SW02}, \figref{SW09}, \figref{SW29}, \figref{SW42}),
  IQ for inclined quads (as in Figure~\figref{SW05}) and CQ for very
  symmetric core quads.
\item Whether the images are unblended.  Distinct unblended images (as
  in Figures~\figref{SW05} and \figref{SW42}) are an advantage in
  modelling, but not essential.
\item Whether all images are discernable.  The topography of an
  arrival-time surface, as encoded by a spaghetti diagram, may require
  more images than are visible.  For example, in Figure~\figref{SW58},
  the modeller has put in a conjectural saddle point near the lensing
  galaxy.
\item Whether the lens is fairly isolated.
\item Whether the arrival-time surface and synthetic image are
  plausible.  In Figure~\figref{SW36} the model implies extra images
  or a long arc, which are not seen.
\item Whether the mass map is reasonable.
\item The halo index $\haloindex$.
\end{enumerate}

@@

@@
